### 2023-01-05 Manuscript/Draft1.Rmd
test

---
csl: canadian-journal-of-fisheries-and-aquatic-sciences.csl
output:
  bookdown::pdf_document2:
    toc: no
    number_sections: no
    fig_caption: yes
    keep_tex: yes
  citation_package: biblatex
  bibliography: IBMWG.bib

  word_document: default
  html_document: default
  pdf_document:
    toc: no
header-includes:
- \usepackage{setspace}
- \doublespacing
- \usepackage{lineno}
- \linenumbers
- \usepackage[belowskip=0pt,aboveskip=0pt]{caption}
 \usepackage{array}
 \usepackage{caption}
 \usepackage{graphicx}
 \usepackage{siunitx}
 \usepackage{colortbl}
 \usepackage{multirow}
 \usepackage{hhline}
 \usepackage{calc}
 \usepackage{tabularx}
 \usepackage{tabulary}
 \usepackage{threeparttable}
 \usepackage{wrapfig}
---

@@

```{r hab-plot1, echo=FALSE,out.width="95%",fig.show='hold', fig.align='center', fig.cap="Visual representation of niche model for Cod."}
knitr::include_graphics(c("Images/hab_snip.png"))
```

>>>>

---
csl: canadian-journal-of-fisheries-and-aquatic-sciences.csl
output:
  bookdown::pdf_document2:
    toc: no
    number_sections: no
    fig_caption: yes
    keep_tex: yes
  pdf_document:
    toc: no
  word_document: default
  html_document: default
bibliography: IBMWG.bib
fontsize: 12pt
header-includes:
- \usepackage{setspace}
- \doublespacing
- \usepackage{lineno}
- \linenumbers
- \usepackage[belowskip=0pt,aboveskip=0pt]{caption}
 \usepackage{array}
 \usepackage{caption}
 \usepackage{graphicx}
 \usepackage{siunitx}
 \usepackage{colortbl}
 \usepackage{multirow}
 \usepackage{hhline}
 \usepackage{calc}
 \usepackage{tabularx}
 \usepackage{tabulary}
 \usepackage{threeparttable}
 \usepackage{wrapfig}
---

@@

```{r hab-plot1, echo=FALSE,out.width="95%",fig.show='hold', fig.align='center', fig.cap="Visual representation of niche model for Cod."}
knitr::include_graphics(c("Images/hab_snip3.png"))
```
